It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-04-12 manuscript/manuscript.qmd
WIP

# Source data preparation script
source(here::here("R/01-data-preparation.R"))

@@

dat_in_sum_day |> 
  ggplot(aes(x = date, y = mean, group = indicator, color = indicator)) +
  geom_point(size = 0.8) +
  geom_line() +
  labs(x = NULL) +
  ylab(bquote(uq/m^3)) +
  facet_wrap(~location, ncol = 4) + 
  scale_y_continuous(limits = c(0, 400)) +
  scale_color_brewer(type = "qual", palette = 2) + 
  theme_bw(base_size = 14) + 
  theme(panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank())

@@

dat_in_ratios |> 
  ggplot(aes(x = date)) +
  geom_linerange(aes(ymin = min, ymax = max)) +
  labs(x = "hour") +
  facet_wrap(~location, ncol = 2)
```

@@

dat_air_quality_sum_who_2021 |> 
  #filter(indicator == "PM~2.5~") |> 
  group_by(location, indicator) |> 
  mutate(exposure_percent = round(exposure_hrs / sum(exposure_hrs) * 100, 0)) |>

@@

    TRUE ~ exposure_percent
  )) |>

@@

ggplot(aes(fill = air_quality_who_annual, values = exposure_percent)) +
  geom_waffle(color ="white", size = 0.5, n_rows = 5, na.rm = TRUE) +
  coord_equal() +
  labs(fill = "WHO 2021 targets (annual)") +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  facet_grid(location ~ indicator, switch = "y") +

  #facet_wrap(~location, ncol = 2) +
  theme_minimal(base_size = 14) +
  # help from: https://stackoverflow.com/questions/34749636/left-justify-text-from-multi-line-facet-labels
  theme(strip.text.x = element_text(hjust = 0),
        strip.text.y = element_text(vjust = 0, size = 4))
```

>>>>

# Source data preparation script

source(here::here("R/00-setup.R"))
source(here::here("R/01-data-preparation.R"))

@@

fig03 <- dat_in_sum_day |> 
  ggplot(aes(x = date, y = mean, group = indicator, color = indicator)) +
  geom_point(size = 0.8) +
  geom_line(alpha = 0.5) +
  labs(x = NULL) +
  ylab(bquote(uq/m^3)) +
  facet_wrap(~location, ncol = 4) + 
  scale_y_continuous(limits = c(0, 400)) +
  scale_color_brewer(type = "qual", palette = 2)

ggsave(filename = "manuscript/figs/fig-03-double-column.tiff",
       plot = fig03,
       dpi = param_dpi,
       width = param_width_double,
       height = param_width_double * width_height_ratio,
       units = "mm")

@@

library(ggplot2)

# create sample data
df <- data.frame(x = 1:10, y = 1:10)

# create plot
ggplot(df, aes(x = x, y = y)) +
  geom_point() +
  xlab(expression(c('PM'[10], 'PM'[2.5])))

fig04 <- dat_in_ratios |> 
  ggplot(aes(x = date)) +
  geom_linerange(aes(ymin = min, ymax = max)) +
  labs(x = "day",
       y = "ratio") +
  facet_wrap(~location, ncol = 2) +
  scale_y_continuous(limits = c(0, 10))

fig04

ggsave(filename = "manuscript/figs/fig-04-double-column.tiff",
       plot = fig04,
       dpi = param_dpi,
       width = param_width_double,
       height = param_width_double * width_height_ratio,
       units = "mm")

@@

percent_exposure <- dat_air_quality_sum_who_2021 |> 
  #filter(indicator == "PM~2.5~") |> 
  group_by(location, indicator) |> 
  mutate(exposure_percent = round(exposure_hrs / sum(exposure_hrs) * 100, 0)) |>

@@

    TRUE ~ exposure_percent
  ))

@@

fig05 <- ggplot(data = percent_exposure,
                aes(fill = air_quality_who_annual, values = exposure_percent)) +
  geom_waffle(color ="white", size = 0.5, n_rows = 5, na.rm = TRUE) +
  coord_equal() +
  labs(fill = "WHO 2021 targets (annual)") +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  facet_grid(location ~ indicator, switch = "y") +

  #facet_wrap(~location, ncol = 2) +
  theme_minimal(base_size = 14) +
  # help from: https://stackoverflow.com/questions/34749636/left-justify-text-from-multi-line-facet-labels
  theme(strip.text.x = element_text(hjust = 0),
        strip.text.y = element_text(vjust = 0, size = 4))

fig05
